Medical Concept Extraction

### 2012-12-17 paper/paper.tex
finished ML background section

\subsubsection{Conditional Random Fields}

>>>>

\subsubsection{Conditional Random Fields}
Conditional random fields (CRF), unlike SVMs, is a probabilistic modeling method. The strength of CRF's in the case of classification for NLP is that it can take neighboring samples (i.e. context) into account when handling individual observations. A CRF is a type of undirected graphical model, which models a conditional probability distribution between observations and output values, which are represented as nodes. Given a sequence of words, this graph takes the form of a chain analogous to a Hidden Markov model. The conditional dependency of each output label on a given input is computed using a feature function in which features are given specific numerical weights and combine to determine the label's likelihood.

We tested our features using an open-source CRF library, CRFSuite \cite{crfsuite}, in addition to our SVMs.
